Dissertation

### 2024-06-21 Sections/HTW.qmd
fix heading on htw page
minor changes
add icons to version links; add igas pdf

_______________________________________________________________________________
{{< fa file-lines >}} [Link to project page](https://tegorman13.github.io/htw/){target="_blank"} \

{{< fa file-pdf >}} [Working Draft of Manuscript](https://tegorman13.github.io/htw/paper.html){target="_blank"}

{{< fa brands github >}} [repo](https://github.com/tegorman13/htw) \
_______________________________________________________________________________

@@

### Variability and Function Learning

@@

## Experiment 1

### Methods

@@

### Analyses Strategy

@@

### Results

@@

## E1 Summary

@@

## Experiment 2

@@

### Methods & Procedure

@@

### Experiment 2 Summary

@@

## Experiment 3

@@

### Experiment 3 Summary

@@

## Computational Model

@@

### ALM & Exam

@@

### Model Fitting

@@

### Modelling Results

@@

*Computational Model Summary*. Across all three experiments, the model fits consistently favored the Extrapolation-Association Model (EXAM) over the Associative Learning Model (ALM). This preference for EXAM was particularly pronounced for participants in the constant training conditions (note the positive coefficients on ModelEXAM:conditVaried interaction terms @tbl-htw-ee-e23). This pattern is clearly illustrated in @fig-htw-best-model, which plots the difference in model errors between ALM and EXAM for each individual participant. Both varied and constant conditions have a greater proportion of subjects better fit by EXAM (positive error differences), with the magnitude of EXAM's advantage visibly larger for the constant group.

>>>>

_______________________________________________________________________________

[{{< fa file-lines >}} Link to project page](https://tegorman13.github.io/htw/){target="_blank"} \

 [{{< fa file-pdf >}} Working Draft of Manuscript](https://tegorman13.github.io/htw/paper.html){target="_blank"}

 [{{< fa brands github >}} repo](https://github.com/tegorman13/htw) \
_______________________________________________________________________________

@@

## Variability and Function Learning

@@

# Experiment 1

## Methods

@@

## Analyses Strategy

@@

## Results

@@

## Experiment 1 Summary

@@

# Experiment 2

@@

## Methods & Procedure

@@

## Experiment 2 Summary

@@

# Experiment 3

@@

## Experiment 3 Summary

@@

# Computational Model

@@

## ALM & Exam

@@

## Model Fitting

@@

## Modelling Results

@@

*Computational Model Summary*.

Across all three experiments, the model fits consistently favored the Extrapolation-Association Model (EXAM) over the Associative Learning Model (ALM). This preference for EXAM was particularly pronounced for participants in the constant training conditions (note the positive coefficients on ModelEXAM:conditVaried interaction terms @tbl-htw-ee-e23). This pattern is clearly illustrated in @fig-htw-best-model, which plots the difference in model errors between ALM and EXAM for each individual participant. Both varied and constant conditions have a greater proportion of subjects better fit by EXAM (positive error differences), with the magnitude of EXAM's advantage visibly larger for the constant group.

### 2024-06-21 Sections/IGAS.qmd
add icons to version links; add igas pdf

---
title: IGAS Project
subtitle: An instance-based model account of the benefits of varied practice in visuomotor skill
#date: last-modified
#page-layout: full
code-fold: true
code-tools: true
toc: true
toc-location: body
toc-title: Contents
toc-depth: 4
format:
  html: default
  hugo-md:
    echo: false
    include: false
    html-math-method: mathjax
    output-file: igas_hugo.md
execute: 
  warning: false
  eval: true
editor: 
  markdown: 
    wrap: 72
---

____________________________________________________
[pdf of the journal
article](Assets/Gorman_Goldstone_2022_Instance-based_model_varied_practice.pdf){target="_blank"}\
[Link to online version of journal
article](https://www.sciencedirect.com/science/article/abs/pii/S0010028522000299){target="_blank"}

>>>>

---
title: IGAS Project
subtitle: An instance-based model account of the benefits of varied practice in visuomotor skill
author:
- name: Thomas E. Gorman
  affiliations: 
  - Department of Psychological and Brain Sciences, Indiana University-Bloomington
  affiliation-url: https://psych.indiana.edu/
  url: https://tegorman13.github.io/
  email: tegorman@iu.edu
  orcid: 0000-0001-5366-5442
page-layout: full
code-fold: true
code-tools: true
toc: true
toc-location: body
toc-title: Contents
toc-depth: 4
format:
  html: default
  hugo-md:
    echo: false
    include: false
    html-math-method: mathjax
    output-file: igas_hugo.md
  hikmah-manuscript-pdf:
    echo: false
    output-file: "igas_dis.pdf"
    mainfont: "Linux Libertine O"
    mainfontoptions:
      - "Numbers=Proportional"
      - "Numbers=OldStyle"
    mathfont: "Libertinus Math"
execute: 
  warning: false
  eval: true
editor: 
  markdown: 
    wrap: 72
prefer-html: true
---

::: {.content-visible when-format="html"}
____________________________________________________

[{{< fa file-pdf >}} pdf of the journal article](https://tegorman13.github.io/pdf/Gorman_Goldstone_2022_Instance-based_model_varied_practice.pdf){target="_blank"}

[{{< fa scroll >}} Link to online version of journal article](https://www.sciencedirect.com/science/article/abs/pii/S0010028522000299){target="_blank"}

[{{< fa brands github >}} repo](https://github.com/tegorman13/IGAS_Variability) \

---

:::

### 2024-06-21 index.qmd
add icons to version links; add igas pdf

[{{< fa file-pdf >}} pdf of the journal
article](Assets/Gorman_Goldstone_2022_Instance-based_model_varied_practice.pdf){target="_blank"}\
[{{< fa scroll >}} Link to online version of journal
article](https://www.sciencedirect.com/science/article/abs/pii/S0010028522000299){target="_blank"}

@@

>>>>

[{{< fa file-pdf >}} pdf of the journal article](https://tegorman13.github.io/pdf/Gorman_Goldstone_2022_Instance-based_model_varied_practice.pdf){target="_blank"}\

[{{< fa scroll >}} Link to online version of journal article](https://www.sciencedirect.com/science/article/abs/pii/S0010028522000299){target="_blank"}

@@

## Full Manuscript

[{{< fa file-lines >}} Web page version](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html)

[{{< fa file-lines >}} Version with code](https://tegorman13.github.io/Dissertation/Sections/full.html)

[{{< fa file-pdf >}} pdf version](https://tegorman13.github.io/Dissertation/paper.html){target="_blank"}\

## Slides

[{{< fa file-lines >}} Slides overview](https://tegorman13.github.io/Dissertation/Presentation/slides.html)

[{{< fa person-chalkboard size=1.0xs >}} Defense slides](https://tegorman13.github.io/Dissertation/Presentation/slides_revealjs.html#/)
